MaBoSS for HPC environments: Implementations of the continuous time Boolean model simulator for large CPU clusters and GPU accelerators

### 2024-02-14 Article.tex
add mpi plots

\begin{figure}%[tbhp]
\centering
\includegraphics[width=.8\linewidth]{Figures/sizek_model.pdf}
\caption{Scalability results for Sizek model}
\label{fig:sizek_results}
\end{figure}

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=.8\linewidth]{Figures/large_model.pdf}
\caption{Scalability results for synthetic model with 1000 nodes}
\label{fig:synthetic_results}
\end{figure}

>>>>

\begin{figure}%[tbhp]
\centering
\includegraphics[width=.8\linewidth]{Figures/sizek_mpi.pdf}
\caption{Scalability results of MPI implementation on Sizek model with 20 cores per MPI node.}
\label{fig:sizek_results}
\end{figure}

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=.8\linewidth]{Figures/synth_mpi_speedup.pdf}
\caption{Speedup scaling of MPI implementation on a synthetic model with 1000 nodes and 32 cores per MPI node.}
\label{fig:synthetic_results}
\end{figure}
